Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-07 sections/conclusion.tex
Fixed Conclusion Citations
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

Based on our comparison of data from a 2.3 m radio telescope, broad-spectrum light sensor, optical livestream, and theoretical data from Stellarium and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
Our result lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by Messerottie, et. al. (2000), and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by Leung et. al. (2021).
In a future study, we will compare these and other results to examine potential sources of uncertainty in the measurements.

>>>>

Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium}\cite{zotti_simulated_2020} and JPL Horizons \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, lying between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
In future work, we will compare these and other results to examine potential sources of uncertainty in our measurements and apparent variance in data.
We will also explore different modeling techniques to further characterize the radio emissions from the Sun.

### 2025-03-07 sections/observations.tex
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and were happy to see that the livestream and theoretical lightcurves overlap quite well.

@@

Because the light sensor data had timestamps included, we used it to confirm the accuracy of our other lightcurves timings.

>>>>

We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and found that the livestream and theoretical lightcurves overlap well.

@@

Because the light sensor data had timestamps included, we used it to confirm the timing accuracy of our other lightcurves.

### 2025-03-07 sections/theoretical.tex
Adding an in-text citation for JPL ephemeris
removed unnessisary citations
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}\cite{zotti_simulated_2020}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve is overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.

@@

In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.
To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System. 
Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
These relationships are also given by Equations 1 through 4.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/RadiovsTheoretical.png}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}

Using these relationships, we can create theoretical lightcurves for varying solar radii.
We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve.
Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

>>>>

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}\cite{zotti_simulated_2020}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.
% Shouldn't we have a figure here?

@@

In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}. 
Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
These relationships are also given by Equations 1 through 4.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/RadiovsTheoretical.png}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}
Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$ by calculating the obscured area of the solar disk at 2000 points in time during the eclipse.
These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve, but it was not a perfect match.
Although the dip in brightness was accurate, the curves show variance in slope.
The theoretical curves assume a uniform disk brightness, not accounting for sunspots or other solar activity.
Nor do they account for limb darkening and how that may change as the obscuration changes throughout the eclipse.
Despite these variances, we found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
This lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by \cite{messerotti_radio_2000}, and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by \cite{leung_solar_2022}.
